---
title: "test"
output: html_document
date: "2023-05-10"
categories: ["Tidymodels"]
tags: ["Packages"]
---

# 1. Observational studies and propensity score ⚖️

-   Conceptual stage
-   Design stage
-   Statistical analysis
-   Summary

## Conceptual

Formulation of the causal question and assumptions using potential
outcomes. Formulated as a randomized experiment.

## Design stage

Reconstruct or approximate the design of a randomized experiment
(independence between treatment assignment and covariates). Needs to
conduct balance diagnostic.

## Statistical analysis

Compare outcomes by treatment. This stage is similar to the standard
model-based analysis.

## Summary

Conclusion based on your estimates.


```{r libraries, message=FALSE}

library(tidyverse) # data manipulation
library(skimr) # Good for descriptive analysis 
library(tidymodels) # modeling
library(gt)  # To create pretty tables
library(table1) # To create pretty tables
tidymodels_prefer() # to avoid problems with two functions with the same name
```

## 1. Conceptual stage

> What is the effect of alcohol consumption on marihuana use?

### Dataset

Selected data from YRBS

```{r load-data}
#load("Causal_inference/small_data.rda")
load("small_data.rda")

small_data  |> skimr::skim()

```

### Demographic variables

-   Age
-   Sex

### Outcome

-   Q46. How old were you when you tried marijuana for the first
    time? A. I have never tried marijuana B. 8 years old or younger C. 9
    or 10 years old D. 11 or 12 years old E. 13 or 14 years old F. 15 or
    16 years old G. 17 years old or older

-   marijuana: recoded as 0 (never used) 1 (used)

### Alcohol use ("Treatment")

-   Q40. How old were you when you had your first drink of alcohol other
    than a few sips? A. I have never had a drink of alcohol other than a
    few sips B. 8 years old or younger C. 9 or 10 years old D. 11 or 12
    years old E. 13 or 14 years old F. 15 or 16 years old G. 17 years
    old or older

-   alcohol: recoded as 0 (never used) 1 (used)

### Questions about drug use

-   Q30. Have you ever tried cigarette smoking, even one or two puffs?
-   Q50. During your life, how many times have you used any form of
    cocaine, including powder, crack, or freebase?
-   Q51. During your life, how many times have you sniffed glue,
    breathed the contents of aerosol spray cans, or inhaled any paints
    or sprays to get high?
-   Q52. During your life, how many times have you used heroin (also
    called smack, junk, or China White)?
-   Q53. During your life, how many times have you used methamphetamines
    (also called speed, crystal meth, crank, ice, or meth)?
-   Q54. During your life, how many times have you used ecstasy (also
    called MDMA)?
-   Q55. During your life, how many times have you taken steroid pills
    or shots without a doctor's prescription?
-   Q56. During your life, how many times have you used a needle to
    inject any illegal drug into your body?
-   Q57. During the past 12 months, has anyone offered, sold, or given
    you an illegal drug on school property?